### 2023-12-13 documentation/thesis/thesis_document.tex
1.4.1

\begin{itemize}
\item
  list of typical low cost hall sensors
\item
  =\textgreater{} alle i2c in der regel
\item ~
  \hypertarget{mechanical-structure}{%
  \section{Mechanical Structure}\label{mechanical-structure}}
\item
  3d druck toleranztest
\item
  magnet halterung mit kraftloser arretierung
\item
  motoren und andere unter umstaänden magnetische teile in der nähe des
  sensors
\item
  nylon schrauben, 3d druck, 3d gedruckte klemmverbindungen
\item
  später rausrechnen durch kalibierung
\end{itemize}

@@

@@

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_fullsphere_sensor.png}
\caption{fullsphere sensor \label{fullsphere_sensor.png}}
\end{figure}

@@

@@

\begin{lstlisting}[language=bash]
    # GET PROXY STATUS
    $ wget http://proxyinstance.local:5556/proxy/status
    {
    "capabilities":[
      "static",
      "axis_b",
      "axis_x",
      "axis_y",
      "axis_z",
      "axis_temp",
      "axis_stimestamp"
   ],
   "commands":[
      "status",
      "initialize",
      "disconnect",
      "combinedsensorcnt",
      "sensorcnt",
      "readsensor",
      "temp"
   ]
   # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
   $ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
   {
   "output":[
      "2"
   ]
}
}
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
    # START PROXY INSTNACE WITH TWO LOCALLY CONNECTED SENSORS
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B
    Proxy started. http://0.0.0.0:5556/
    PRECHECK: SENSOR_HAL: 1337 # SENSOR A FOUND
    PRECHECK: SENSOR_HAL: 4242 # SENSOR B FOUND
    Terminate  [Y/n] [y]: 
\end{lstlisting}

@@

\begin{itemize}
\tightlist
\item
  alle clients über ptp verbunden
\item
  zentraler reset zwischen zwei pps pulsen um den readout counter auf 0
  zu setzten
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  list of typical low cost hall sensors
\item
  =\textgreater{} alle i2c in der regel
\item
\end{itemize}

\hypertarget{mechanical-structure}{%
\section{Mechanical Structure}\label{mechanical-structure}}

\begin{itemize}
\tightlist
\item
  3d druck toleranztest
\item
  magnet halterung mit kraftloser arretierung
\item
  motoren und andere unter umstaänden magnetische teile in der nähe des
  sensors
\item
  nylon schrauben, 3d druck, 3d gedruckte klemmverbindungen
\item
  später rausrechnen durch kalibierung
\end{itemize}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Sensors_CL-Interface.png}
\caption{Sensors CL-Interface \label{Sensors_CL-Interface.png}}
\end{figure}

\begin{figure}
\centering
\includegraphics{./generated_images/border_Query_sensors_b_value_using_CLI.png}
\caption{Query sensors b value using CLI
\label{Query_sensors_b_value_using_CLI.png}}
\end{figure}

@@

\hypertarget{sensor-syncronsisation}{%
\section{\texorpdfstring{Sensor Syncronsisation
\label{CHAPTER_Sensor_Syncronsisation}}{Sensor Syncronsisation }}\label{sensor-syncronsisation}}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_1D_sensor_contrsuction_with_universal_magnet_mount.png}
\caption{1D sensor contrsuction with universal magnet mount
\label{1D_sensor_contrsuction_with_universal_magnet_mount.png}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}
\caption{Full-Sphere sensor implementation using two Nema17 stepper
motors in a polar coordinate system
\label{Full-Sphere_sensor_implementation_using_two_Nema17_stepper_motors_in_a_polar_coordinate_system.png}}
\end{figure}

@@

\begin{lstlisting}[language=bash]
    # GET PROXY STATUS
    $ wget http://proxyinstance.local:5556/proxy/status
    {
    "capabilities":[
      "static",
      "axis_b",
      "axis_x",
      "axis_y",
      "axis_z",
      "axis_temp",
      "axis_stimestamp"
   ],
   "commands":[
      "status",
      "initialize",
      "disconnect",
      "combinedsensorcnt",
      "sensorcnt",
      "readsensor",
      "temp"
   ]

   # RUN A SENSOR COMMAND AND GET THE TOTAL SENSOR COUNT
   $ wget http://proxyinstance.local:5556/proxy/command?cmd=combinedsensorcnt
   {
   "output":[
      "2"
   ]
}
}
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
    # CONFIGURE MEASUREMENT JOB USING A PROXY INSTANCE
    $ python3 mrpproxy.py proxy launch /dev/ttySENSOR_A /dev/ttySENSOR_B

\end{lstlisting}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the USB interface. If several
sensors are connected locally, they can be connected to each other via
their sync input using short cables. One sensor acts as the central
clock (see chapter \ref{CHAPTER_Sensor_Syncronsisation}). However, this
no longer works for long distances and a diversion must be made via the
network connection.

If time-critical synchronisation is required, PTP and PPS functionality
can be used on many single-board computers (such as the RaspberryPi
Compute Module).

\begin{itemize}
\tightlist
\item
  was ptp, bild pps output
\item
  alle clients über ptp verbunden
\item
  dso bild von jeff gerling über rpi4 ptp
\end{itemize}
